Adopting agile in the large: motivations, success factors and challenges

### 2014-05-04 journal/article.tex
Misunderstandings in the agile model

A challenge many organizations came across was that an agile model was not
straight forward to implement.

@@

>>>>

A challenge most organizations came across was that an agile model was difficult
implement. An experienced software team may do well in training, but when the
time comes to apply agile techniques in practice the team may get lost [P21].
Agile was also seen as a solution to all problems [P9], success was declared
prematurely [P49], and expectations created by successful early experiments were
not fullfilled [P38]. Disapointment was granted when these hopes were not
fullfilled and implementing an agile model was found to be hard and time
consuming. The difficulty in implementing agile is evident in misconceptions of
the agile model, when by-the-book implementations prove to be insufficient, and
when the agile methods were applied badly to the organization.

There were many examples on problems caused by misconceptions of what agile
software development is. On a general level, Bang [P4] describes how the values
of the agile manifesto were not understood, and agile practices were carried out
without understanding their purpose. In one case management saw the purpose of
agile simply being faster product delivery [P9].

On a team level there were several examples of misunderstanding the agile model.
Cases describe how agile was seen as freedom to hack without documentation
[P26], that development could be done without design tasks [P37], and that agile
meant that everyone should become a generalist [P42]. Schatz and Abdelshafi
describe how teams presented unfinished work at reviews and ignored the
principle of showing only completed increments, which resulted in a backlog of
bugs [P44]. In one case team members had perceived the introduction of agile as
a means to squeeze out more efficiency [P45]. In addition, the flatter
organization was seen as fewer career opportunities, and pushed team members to
internal competition for visibility [P45].
Still one misunderstanding of agile was due to perceiving it only through the
tools used, such as project management software [P48]. Superficial focusing only
on tools themselves and not the reasons behind their use led to frustration
[P42].

% Misunderstandings in the agile model

% By the book is not good

% Customizing badly (mapping to old model)

% Differing vocabularies

% Roles of managers

@@

% Roles of managers (continued)
